---
title: "Epidemiology of helminth and protozoan parasites in Dosso Region, Niger"
author: "Jacqueline Maasch & Kristen Aiemjoy"
date: "3/19/20"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Load packages: tidyverse, xtable, stargazer, ggthemes, etc.
```{r packages, echo = FALSE, message = FALSE}
library(tidyverse)
library(lubridate)
library(epiR)
library(scales)
library(bazar)
library(gmodels)
library(xtable)
library(stargazer)
library(ggthemes)

#For anthropometry and z-scores.
library(zscorer)
library(viridis)
library(ggridges)
library(lme4)
library(lmerTest)


```

Set working directories. Set one directory to comment depending on who is working on the file.
```{r directory}
# Kristen: 
#setwd(redacted)

# Jaqueline:
#setwd(redacted)
```

Load data. Merged file prepared in "GiardiaDataPrep_03.20.20.R".
```{r data}
d <- read.csv("~/Dropbox/_Papers/Niger parasite epi/Data/Anthro data merge/GiardiaAnthroSchistoMerged_03.20.20.csv") %>%
  rowwise() %>%
  mutate(HeightM = median(Height.1, Height.2, Height.3), 
         WeightM = median(Weight.1, Weight.2, Weight.3)) %>%
  ungroup() %>%
  mutate(WeightM.kg = ifelse(Weight.Unit == "Pounds", WeightM/2.205, WeightM),
         sex = as.numeric(fct_recode(gender, "1"="MALE", "2"="FEMALE")),
         standing = fct_recode(Height.Method, standing="HEIGHT", supine= "LENGTH"),
         ageD = ageM*30,
         loosewatMother = fct_collapse(Sample.Consistency.Mother,
                                       "loose/watery" = c("Watery", "Fluffy With Ragged Edges"),
                                       "formed" = c("Lumpy", "Smooth Soft", "Separate Hard Lumps")),
         stoolPos = ifelse(stool1_pos==1 | stool2_pos ==1, 1, 0))



## Data for Gates Open Research
d.gor <- d %>%
  mutate(ID = 1:n()) %>%
  rename(Community = vilID,
         giardiaPos = truePos) %>%
  mutate(schistoHPos = ifelse(is.na(St1_schisto_pos), 0, St1_schisto_pos),
         ancylostomaPos=0,
         ascarisPos = 0,
         schistoMPos = 0,
        trichurisPos = 0) %>%
  select(ID, gender, ageY, ageM, Community, giardiaPos, schistoHPos, schistoMPos, ancylostomaPos, ascarisPos, trichurisPos,
         Height.1, Height.2, Height.3, Height.Method, 
  Weight.1, Weight.2, Weight.3, Weight.Unit)
  
write_csv(d.gor, "NigerParasitePCR.csv")

```


Anthropometry.
```{r anthro}
#Weight for height.
d <- addWGSR(data = d, sex = "sex", firstPart = "WeightM.kg", 
               secondPart = "HeightM", index = "wfh", standing="standing")

#Weight for age.
d <- addWGSR(data = d, sex = "sex", firstPart = "WeightM.kg", 
               secondPart = "ageD", index = "wfa")

#Height for age.
d <- addWGSR(data = d, sex = "sex", firstPart = "HeightM", 
               secondPart = "ageD", index = "hfa", standing="standing")


# svy <- svy %>%
#   mutate(ZCat = cut(wfhz, c(-Inf,-3, -2, -1, 0, Inf), labels=c("<-3", "-3,-2", "-2,-1", "-1,0", "0+")) ) 
```


Abstract results
```{r}
#giardia positive
table(d$stool1_pos)
56/86


table(d$ageY, d$stool1_pos)

15/17

d %>% group_by(vilID) %>% summarise(n=n())


```
Results text: 
```{r}

#All villages.
levels(d$vilID)

#Mean age in months.
summary(d$ageM)

#Mean/median age in years.
summary(d$ageY)

#Number male and female.
table(d$gender)


Table1_b <- d %>%
    summarize(nChildren = n(), 
    nVil = length(unique(vilID)), 
    MedianAge = round(median(ageY, na.rm = T), 2), 
    Age.p25 = round(quantile(ageY, na.rm =T,  probs=.25), 2),
    Age.p75 = round(quantile(ageY, na.rm = T, probs=.75), 2),
    prop.female=round(100*mean(gender == "FEMALE",  na.rm=TRUE),1),
    nFemale = sum(gender=="FEMALE", na.rm=TRUE)) %>%
    mutate(
    Female = paste(nFemale," (",prop.female,"% )", sep=""),
    MedianAge = paste(MedianAge, " (", Age.p25, "-", Age.p75 , ")", sep="")) %>%
    select(nChildren, nVil, MedianAge, Female) %>%
    t %>% #transpose
    as.data.frame() %>%
    `colnames<-`(c("Overall")) 


#paragraph 2
d %>% group_by(vilID) %>% 
  summarise(n= n(), 
            nPos = sum(stool1_pos), 
            prb = nPos/n)

56/86

2217/3420
359/2217
```




Child growth z-score results 2.
```{r zscore2}
mean(d$hfaz)
sd(d$hfaz)

mean(d$wfaz)
sd(d$wfaz)

round(mean(d$wfhz), 2)
round(sd(d$wfhz), 3)

t.test(hfaz~stool1_pos, data=d)
t.test(wfaz~stool1_pos, data=d)
t.test(wfhz~stool1_pos, data=d)


# library(lmerTest)
# mod <- lmer(wfhz ~ stool1_pos + (1|vilID), data = d)
# anova(mod)
# summary(mod)

library(geepack)
library(broom)


mod <- geeglm(hfaz ~ stool1_pos + ageM, id = vilID, data = d)
broom::tidy(x = mod, conf.int = TRUE)

mod <- geeglm(wfaz ~ stool1_pos + ageM, id = vilID, data = d)
broom::tidy(x = mod, conf.int = TRUE)


mod <- geeglm(wfhz ~ stool1_pos + ageM, id = vilID, data = d)
broom::tidy(x = mod, conf.int = TRUE)
```



Age/prevalence sex results.
```{r ageSexData}
d %>% group_by(ageY, gender) %>%
  summarise(prev = mean(truePos), 
            n = n(),
            se = sd(truePos)/sqrt(n),
            lCI = prev-1.96*se, 
            uCI = prev+1.96*se)

d %>% group_by(ageY) %>%
  summarise(prev = mean(truePos), 
            n = n(),
            nPos = sum(stool1_pos))

(1/25)*100
1/86
```


Bar chart of child age and sex with y-axis as infection prevalence rate.
```{r}
dAgeSexPrev2 <- d %>% 
  group_by(ageY, gender) %>%
  summarise(prev = (mean(truePos))*100,
            n = n(),
            se = sd(truePos)/sqrt(n),
            lCI = prev-1.96*se, 
            uCI = prev+1.96*se)

dAgeSexPrev2 <- d %>% 
  group_by(ageY, gender) %>%
  summarise(prev =  mean(truePos, na.rm = TRUE),
            n = n(),
            N_notMiss = sum(!is.na(truePos)),
            sd = sd(truePos, na.rm=TRUE)) %>%
            mutate(SE = sd/sqrt(N_notMiss), 
                   lowerCI = prev - 1.96*SE, 
                   upperCI = prev + 1.96*SE,
                   upperCI = replace(upperCI, upperCI>1, 1),
                   lowerCI = replace(lowerCI, lowerCI<0, 0))

barAgeSexPrev <- ggplot(dAgeSexPrev2, aes(x = ageY, y = prev, fill = gender)) + 
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = lowerCI, ymax = upperCI), width = 0.2,
                position = position_dodge(0.9), alpha = 0.5) +
  theme_hc() +
  theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 12), 
        plot.title = element_text(size = 12, 
                                    face = "bold", 
                                    hjust = 0.5), 
        legend.title = element_text(size = 10),
        legend.direction = "vertical",
        legend.position = "right",
        panel.grid.major.x = element_blank()) +
  scale_y_continuous(labels = percent, limits = c(0,1), expand = c(0,0)) +
  labs (y= "Infection prevalence\n", 
        x = "\nChild age in years", 
        fill = "", 
        title = "") +
  scale_fill_manual(values = c("#E5DDCB", "#D1937D"), 
                    label = c("Female", "Male")) +
  #geom_text(aes(label = c("6/11", "10/20", "14/17", "9/11", "18/25"))) 
  annotate("text", x = 0, y = .1, 
           label = "6/11\n54.5%", size = 3.5, color = "black") + 
  annotate("text", x = 1, y = .1, 
           label = "10/20\n50.0%", size = 3.5, color = "black") + 
  annotate("text", x = 2, y = .1, 
           label = "14/17\n82.4%", size = 3.5, color = "black") + 
  annotate("text", x = 3, y = .1, 
           label = "9/11\n81.8%", size = 3.5, color = "black") + 
  annotate("text", x = 4, y = .1, 
           label = "18/25\n72.0%", size = 3.5, color = "black")

barAgeSexPrev

#ggsave("/Users/razel/Dropbox/Niger parasite epi/Data/Exported figures/prev_age_sex.jpg", plot = last_plot(), width = 8, height = 6, dpi = 1000)
```





Schisto positive individual.
```{r schisto}
dSchisto <- d %>%
  filter(St1_schisto_ct != 19.41028)
```
